Assertion Contracts

### 2022-01-11 papers/assertion-contract/paper.tex
Add files via upload

If any of the validators finds a violation of the assertion, the final transaction (call) is aborted. In our approach, the validator make an effor to find a counterexample for the assertion offline. Therefore, the validators interact with the smart contract to submit a  counterexample or a computation proof through smart contract function calls. 
\subsection{Smart Contract's Functions and Storage}
\subsubsection{Functions}
There can be several functions in a contract, we consider here the functions where one of the parameters must be validated. Because the parameter must be checked before the actual work can be done, we separate it into two functions: a caller first invokes an assertion function to pass the parameter for  verification and after the parameter is verified, a normal function with a assumion that a paramete is valid can be called to do the actual work.  A contract must contain the following three types of functions:

@@

\subsubsection{Offline Assertion Program}
To check the validity of a parameter, each validator independently runs aassertion program that generates a negation formula for the parameter and then selects a random point in the parameter range to find a counterexample. The assertion program should be sent to all validators and should be executed offline from the blockchain network. In addition, the program must provide a proof of computation that can be submitted to the blockchain to receive an award. This trigger computation proof should be generated identically for each run. In the following part, you will learn more about the offline assertion program.
\begin{figure}
\centering
\includegraphics[scale=.6]{assertion_1}
\caption{Assertion Contract Ptotocol (1)}
\end{figure}

\subsection{Roles}
\subsubsection{Managing the contract and offline assertion program.}
A contract is provided by its owner on the blockchain. In addition to the code of the contract on the blockchain, there is an offline assertion program to find a counterexample for a submitted parameter, and this code should be available to all validators. Let us discuss two ways to distribute this offline assertion program.

\begin{itemize} 
\item The program code is stored inside the contract code. In this case, the code is available on the blockchain. However, it could be expensive to store the code on the blockchain, and especially impossible if the program is very large. (For discussion: and can be sent as data in a normal transfer?). 
\item The program code is stored offline and should always be available to callers/validators upon request. There are two ways to make it available to validators: (1) the program is stored on a source that can be accessed by the caller/validator, or the owner can make it available on request, which is sent to a caller/validator on request, and (2) when a caller invokes an assertion function, it should send the program to the network via messaging systems such as waku in eutherum, or the owner should broadcast it to the network when deplying the contract, and in this case interested validators should store the code locally. \end{itemize}

@@

\paragraph{Submitting the parameter.} A caller passes the parameter to be checked by calling an assertion function. The function then stores all the necessary information, namely the parameter hash in Figure 1 (or the parameter in Figure 2), the caller's address, and the timestamp in memory as if in a record. The parameter's record also contains initial information to monitor the progress of the parameter's verification, e.g., how many computational proofs have been presented, whether a counterexample has been found, etc. This information is used to review a proof or counterexample presented by a validator, and to decide when a work function can be called for that parameter. The caller can then send this information along with the offline assertion program to all validators via a messaging system.

@@

\subsubsection{Validating a parameter}
When a parameter is sent to an validator, the validator runs the offline assertion program to find a counterexample. If so, the validator submits the parameter to the blockchain to receive a reward. Otherwise, a computation proof is submitted, which should be automatically generated when the program is executed. A validator interacts with the contract in two ways: he can announce a counterexample and submit a calculation proof. The validator must clarify which parameter is being verified by submitting the parameter, the address of the caller, and the timestamp. This information is then matched with the records in the storage.

\paragraph{Submission of proof.} After running the program but finding no counterexample, the validator submits a computational proof to receive a reward for running the check. The proof should be unique for each run. Since the offline assertion program is the same for every validators, we need the address of the validator for each parameter to make the proof unique for each validator. This prevents the validator from copying a calculation proof from others. Also, since the proof cannot be stored in the blockchain or it would be too costly, a timestamp is added for the execution of the program to prevent an validator from using the same proof for multiple submission. Therefore, the proof should be generated from the program and is calculated based on the parameter's information provided. Each validator who runs the program enters the parameter, the address of the caller, the timestamp, and the time at which he or she runs the program, as well as his or her address. This information is used to calculate an unique computation proof.
\paragraph{Asserting a counterexample.} a validator can submit a counterexample and that counterexample is then verified by the contract on the blockchain. If it is correct, there is an award to the validator and the function updates the store accordingly. There are two options: update the status or delete the record.

(For discussion: what happens if the parameter was checked but not executed by the contract caller. It will occupy the memory forever. Since a function is passive in this case, there should be a mode (function) executed by the owner to delete this parameter after some time. Also, the program is executed to check the parameter to find a counterexample. So basically it generates a random number (since it is offline, why do not we run the entire check - safe time) a limited number of proofs while it runs the check).

When the normal function is called by the check function, the storage stores the parameter in place of its hash and any other parameters required for the normal function. If certain requirements are met, the function is called when a validator submits the proof.

>>>>

If any of the validators finds a violation of the assertion, the final transaction (call) is aborted. In our approach, the validator make an effor to find a counterexample for the assertion off-chain. Therefore, the validators interact with the smart contract to submit a  counterexample or a computation proof through smart contract function calls. 
\subsection{Smart Contract's Functions and Storage}
\subsubsection{Functions}
There can be several functions in a contract, we consider here the functions where one of the parameters must be validated. Because the parameter must be checked before the actual work can be done, we separate it into two functions: a caller first invokes an assertion function to pass the parameter for  verification and after the parameter is verified, a normal function with a assumion that a paramete is valid can be called to do the actual work.  A contract must contain the following three types of functions:

@@

\subsubsection{Off-chain Assertion Program}
To check the validity of a parameter, each validator independently runs aassertion program that generates a negation formula for the parameter and then selects a random point in the parameter range to find a counterexample. The assertion program should be sent to all validators and should be executed off-chain from the blockchain network. In addition, the program must provide a proof of computation that can be submitted to the blockchain to receive an award. This trigger computation proof should be generated identically for each run. In the following part, you will learn more about the off-chain assertion program.
\begin{figure}
\centering
\includegraphics[scale=.6]{assertion_1}
\caption{Assertion Contract Ptotocol (1)}
\end{figure}

\subsection{Roles}
\subsubsection{Managing the contract and off-chain assertion program.}
A contract is provided by its owner on the blockchain. In addition to the code of the contract on the blockchain, there is an off-chain assertion program to find a counterexample for a submitted parameter, and this code should be available to all validators. Let us discuss two ways to distribute this off-chain assertion program.

\begin{itemize} 
\item The program code is stored inside the contract code. In this case, the code is available on the blockchain. However, it could be expensive to store the code on the blockchain, and especially impossible if the program is very large. (For discussion: and can be sent as data in a normal transfer?). 
\item The program code is stored off-chain and should always be available to callers/validators upon request. There are two ways to make it available to validators: (1) the program is stored on a source that can be accessed by the caller/validator, or the owner can make it available on request, which is sent to a caller/validator on request, and (2) when a caller invokes an assertion function, it should send the program to the network via messaging systems such as waku in eutherum, or the owner should broadcast it to the network when deplying the contract, and in this case interested validators should store the code locally. \end{itemize}

@@

\paragraph{Submitting the parameter.} A caller passes the parameter to be checked by calling an assertion function. The function then stores all the necessary information, namely the parameter hash in Figure 1 (or the parameter in Figure 2), the caller's address, and the timestamp in memory as if in a record. The parameter's record also contains initial information to monitor the progress of the parameter's verification, e.g., how many computational proofs have been presented, whether a counterexample has been found, etc. This information is used to review a proof or counterexample presented by a validator, and to decide when a work function can be called for that parameter. The caller can then send this information along with the off-chain assertion program to all validators via a messaging system.

@@

\subsubsection{Validating a parameter}
When a parameter is sent to an validator, the validator runs the off-chain assertion program to find a counterexample. If so, the validator submits the parameter to the blockchain to receive a reward. Otherwise, a computation proof is submitted, which should be automatically generated when the program is executed. A validator interacts with the contract in two ways: he can announce a counterexample and submit a calculation proof. The validator must clarify which parameter is being verified by submitting the parameter, the address of the caller, and the timestamp. This information is then matched with the records in the storage.

\paragraph{Submission of proof.} After running the program but finding no counterexample, the validator submits a computational proof to receive a reward for running the check. The proof should be unique for each run. Since the off-chain assertion program is the same for every validators, we need the address of the validator for each parameter to make the proof unique for each validator. This prevents the validator from copying a calculation proof from others. Also, since the proof cannot be stored in the blockchain or it would be too costly, a timestamp is added for the execution of the program to prevent an validator from using the same proof for multiple submission. Therefore, the proof should be generated from the program and is calculated based on the parameter's information provided. Each validator who runs the program enters the parameter, the address of the caller, the timestamp, and the time at which he or she runs the program, as well as his or her address. This information is used to calculate an unique computation proof.
\paragraph{Asserting a counterexample.} a validator can submit a counterexample and the counterexample is then checked by the contract on the blockchain. If it is correct, there is an award to the validator and the function updates the store accordingly. There are two options: update the status or delete the record.

(For discussion: what happens if the parameter was checked but not executed by the contract caller. It will occupy the memory forever. Since a function is passive in this case, there should be a mode (function) executed by the owner to delete this parameter after some time. Also, the program is executed to check the parameter to find a counterexample. So basically it generates a random number (since it is off-chain, why do not we run the entire check - safe time) a limited number of proofs while it runs the check).

When the normal function is called by the validate function, the storage stores the parameter in place of its hash and any other parameters required for the normal function. If certain requirements are met, the function is called when a validator submits the proof.
